Practical Machine Learning - Prediction Assignment Writeup
========================================================
```{r echo=FALSE}
options(warn=-1)
```


Download the training and test data and load them to variables `Train` and `Test`, respectively.
```{r results="hide"}
setInternet2(TRUE)
download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", 
              destfile="Train.csv")
download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv",
              destfile="Test.csv")
Train <- read.csv("Train.csv")
Test <- read.csv("Test.csv")
```

Clean the data by removing columns with more than 80% NAs, X and raw timestamps:
```{r}
ind <- which(colSums(is.na(Test))/nrow(Test)>0.8)
Test2 <- Test[,c(-1,-3,-4,-ind)]
Train2 <- Train[,c(-1,-3,-4,-ind)]
Train2 <- Train2[complete.cases(Train2),]
```

Train with Trees with 10-fold cross validation
```{r results="hide"}
library(caret)
tc <- trainControl("cv",10)
rpart.grid <- expand.grid(.cp=0.01)
modTree <- train(classe~., method="rpart", data=Train2, trControl=tc, tuneGrid=rpart.grid)
```

The tree model:
```{r}
modTree
```

Since the accuracy is about 80% by 10-fold cross validation, we expect the out-of-sample error to be about 20%.

Predictions:
```{r}
predict(modTree,newdata=Test2)
```




**References**

Ugulino, W.; Cardador, D.; Vega, K.; Velloso, E.; Milidiu, R.; Fuks, H. Wearable Computing: Accelerometers' Data Classification of Body Postures and Movements. Proceedings of 21st Brazilian Symposium on Artificial Intelligence. Advances in Artificial Intelligence - SBIA 2012. In: Lecture Notes in Computer Science. , pp. 52-61. Curitiba, PR: Springer Berlin / Heidelberg, 2012. ISBN 978-3-642-34458-9. DOI: 10.1007/978-3-642-34459-6_6. 